---
title: "Exploratory Analysis"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'exploratory_analysis.html'))})
---


#### Define Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE}
library("stringr")
library("dplyr")
library("ggplot2")
library("gridExtra")
library("knitr")
library("vegan")
library("magrittr")
```

#### Define Path
```{r tidy=TRUE}
dir.wrk <- getwd()
dir.data <- file.path(dir.wrk, "dataset/data")
dir.annot <- file.path(dir.wrk, "dataset/annotation")
```
#### Define Files
```{r tidy=TRUE}
file.dat <- file.path(dir.data, "mastertbl_household_reconstruction.tsv")
```

#### Load Data
```{r tidy=TRUE}
dat <- read.delim(file.dat, header=TRUE, stringsAsFactors=FALSE)

# FACTORIZE ---
dat$DISTRICT <- factor(dat$DISTRICT, levels=c("Dhading","Sindhupalchowk"))
dat$VDC_MUN <- factor(dat$VDC_MUN, levels=c("Gumdi","Sertung","Batase","Pangtang"))
dat$WARD <- as.factor(dat$WARD)
dat$SEX <- factor(dat$SEX, levels=c("Male","Female"))
dat$ETHNICITY <- factor(dat$ETHNICITY, levels=c("Bahun","Chhetri","Dalit-Others","Gurung-Magar","Newar","Tamang"))
dat$EDUCATION_LEVEL <- factor(dat$EDUCATION_LEVEL, levels=c("Illiterate","Primary","Secondary","University"))
dat$OCCUPATION <- factor(dat$OCCUPATION, levels=c("Agriculture","Business","Goverment Employee","Labour","Teacher"))
dat$INCOME_LEVEL <- factor(dat$INCOME_LEVEL, levels=c("0-2.5K","2.5-10K","10-20K","20-40K","40-60K","60K-Above"))
dat$RECON_COMPLETED <- as.factor(dat$RECON_COMPLETED)
dat$FREEDOM_CHOICE <- as.factor(dat$FREEDOM_CHOICE) 

#str(dat)
```
</br></br>

### Generate Basic Statistics 
</br>

#### Overall Satisfaction Level
```{r}
dm <- dat %>% 
          dplyr::summarize(Satisfaction_Mean=round(mean(SATISFACTION_LEVEL),3), 
                    Satisfaction_Median=round(median(SATISFACTION_LEVEL),3), 
                    Satisfaction_SD=round(sd(SATISFACTION_LEVEL),3))

knitr::kable(dm)
```
</br>


#### Distribution by Location
```{r}
df11 <- dat %>% 
          dplyr::count(DISTRICT, sort=FALSE, name="Number_of_Households")

df12 <- dat %>% 
          dplyr::select(DISTRICT, SATISFACTION_LEVEL) %>%
          group_by(DISTRICT) %>%
          summarize(Satisfaction_Mean=round(mean(SATISFACTION_LEVEL),3), 
                    Satisfaction_Median=round(median(SATISFACTION_LEVEL),3), 
                    Satisfaction_SD=round(sd(SATISFACTION_LEVEL),3))

df1 <- merge(df11, df12, by="DISTRICT")

knitr::kable(df1)
```

</br>

#### Distribution by Sex
```{r}
df21 <- dat %>% 
          dplyr::count(SEX, sort=FALSE, name="Number_of_Households")

df22 <- dat %>% 
          dplyr::select(SEX, SATISFACTION_LEVEL) %>%
          group_by(SEX) %>%
          summarize(Satisfaction_Mean=round(mean(SATISFACTION_LEVEL),3), 
                    Satisfaction_Median=round(median(SATISFACTION_LEVEL),3), 
                    Satisfaction_SD=round(sd(SATISFACTION_LEVEL),3))

df2 <- merge(df21, df22, by="SEX")

knitr::kable(df2)
```

</br>

#### Distribution by Ethnicity
```{r}
df31 <- dat %>% 
          dplyr::count(ETHNICITY, sort=FALSE, name="Number_of_Households")

df32 <- dat %>% 
          dplyr::select(ETHNICITY, SATISFACTION_LEVEL) %>%
          group_by(ETHNICITY) %>%
          summarize(Satisfaction_Mean=round(mean(SATISFACTION_LEVEL),3), 
                    Satisfaction_Median=round(median(SATISFACTION_LEVEL),3), 
                    Satisfaction_SD=round(sd(SATISFACTION_LEVEL),3))

df3 <- merge(df31, df32, by="ETHNICITY")

knitr::kable(df3)
```

</br>

#### Distribution by Income Level
```{r}
df41 <- dat %>% 
          dplyr::count(INCOME_LEVEL, sort=FALSE, name="Number_of_Households")

df42 <- dat %>% 
          dplyr::select(INCOME_LEVEL, SATISFACTION_LEVEL) %>%
          group_by(INCOME_LEVEL) %>%
          summarize(Satisfaction_Mean=round(mean(SATISFACTION_LEVEL),3), 
                    Satisfaction_Median=round(median(SATISFACTION_LEVEL),3), 
                    Satisfaction_SD=round(sd(SATISFACTION_LEVEL),3))

df4 <- merge(df41, df42, by="INCOME_LEVEL")

knitr::kable(df4)
```

</br>

#### Distribution by Education Level
```{r}
df51 <- dat %>% 
          dplyr::count(EDUCATION_LEVEL, sort=FALSE, name="Number_of_Households")

df52 <- dat %>% 
          dplyr::select(EDUCATION_LEVEL, SATISFACTION_LEVEL) %>%
          group_by(EDUCATION_LEVEL) %>%
          summarize(Satisfaction_Mean=round(mean(SATISFACTION_LEVEL),3), 
                    Satisfaction_Median=round(median(SATISFACTION_LEVEL),3), 
                    Satisfaction_SD=round(sd(SATISFACTION_LEVEL),3))

df5 <- merge(df51, df52, by="EDUCATION_LEVEL")

knitr::kable(df5)
```

</br>

#### Distribution by Reconstruction Completed Level
```{r}
df61 <- dat %>% 
          dplyr::count(RECON_COMPLETED, sort=FALSE, name="Number_of_Households")

df62 <- dat %>% 
          dplyr::select(RECON_COMPLETED, SATISFACTION_LEVEL) %>%
          group_by(RECON_COMPLETED) %>%
          summarize(Satisfaction_Mean=round(mean(SATISFACTION_LEVEL),3), 
                    Satisfaction_Median=round(median(SATISFACTION_LEVEL),3), 
                    Satisfaction_SD=round(sd(SATISFACTION_LEVEL),3))

df6 <- merge(df61, df62, by="RECON_COMPLETED")

knitr::kable(df6)
```

</br>

#### Distribution by Freedom of Choice
```{r}
df71 <- dat %>% 
          dplyr::count(FREEDOM_CHOICE, sort=FALSE, name="Number_of_Households")

df72 <- dat %>% 
          dplyr::select(FREEDOM_CHOICE, SATISFACTION_LEVEL) %>%
          group_by(FREEDOM_CHOICE) %>%
          summarize(Satisfaction_Mean=round(mean(SATISFACTION_LEVEL),3), 
                    Satisfaction_Median=round(median(SATISFACTION_LEVEL),3), 
                    Satisfaction_SD=round(sd(SATISFACTION_LEVEL),3))

df7 <- merge(df71, df72, by="FREEDOM_CHOICE")
df7$FREEDOM_CHOICE <- as.numeric(df7$FREEDOM_CHOICE)
df7 <- df7[order(df7$FREEDOM_CHOICE, decreasing=FALSE),]

knitr::kable(df7)
```

### Correlation between mean and SD of satisfaction:by Ethnicity
```{r}
shapiro.test(df3$Satisfaction_Mean)
shapiro.test(df3$Satisfaction_SD)
cor.test(df3$Satisfaction_Mean, df3$Satisfaction_SD, method="pearson")
```

### Correlation between mean and SD of satisfaction:by Income
```{r}
shapiro.test(df4$Satisfaction_Mean)
shapiro.test(df4$Satisfaction_SD)
cor.test(df4$Satisfaction_Mean, df4$Satisfaction_SD, method="pearson")
```

### Correlation between mean and SD of satisfaction:by Education
```{r}
shapiro.test(df5$Satisfaction_Mean)
shapiro.test(df5$Satisfaction_SD)
cor.test(df5$Satisfaction_Mean, df5$Satisfaction_SD, method="pearson")
```

</br>

### Distribution of Satisfaction Level
```{r}
p1 <- ggplot(dat, aes(x=SATISFACTION_LEVEL)) +
        geom_histogram(aes(y=..density..), position="identity", color="#FFFFFF", fill="#377eb8", bins=10) +
        scale_x_continuous(breaks=seq(0,10,by=1)) +
        theme(
          axis.text.x = element_text(size = 10, color="#000000"),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title.x = element_text(size = 10, color="#000000"),
          axis.title.y = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000"),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 12, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "none") +
        geom_density(alpha=.2)+ 
        ylab("Probability  Density") +
        xlab("Satisfaction Level") + 
        ggtitle("")
```

```{r fig.height = 3, fig.width = 8, fig.align = "center"}
p1
```

#### Distribution of Satisfaction Level (by Ethnicity)
```{r}
p2 <- ggplot(dat, aes(x=SATISFACTION_LEVEL)) +
        geom_histogram(aes(y=..density..), position="identity", color="#FFFFFF", fill="#377eb8", bins=10) +
        scale_x_continuous(breaks=seq(0,10,by=1)) +
        facet_wrap(~ETHNICITY, nrow=2, scales="fixed") +
        theme(
          axis.text.x = element_text(size = 10, color="#000000"),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title.x = element_text(size = 10, color="#000000"),
          axis.title.y = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000", hjust=0.5),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "none") +
        geom_density(alpha=.2)+ 
        ylab("Probability  Density") +
        xlab("Satisfaction Level") + 
        ggtitle("")
```

```{r fig.height = 4, fig.width = 10, fig.align = "center"}
p2
```

#### Distribution of Satisfaction Level (by Sex)
```{r}
p3 <- ggplot(dat, aes(x=SATISFACTION_LEVEL)) +
        geom_histogram(aes(y=..density..), position="identity", color="#FFFFFF", fill="#377eb8", bins=10) +
        scale_x_continuous(breaks=seq(0,10,by=1)) +
        facet_wrap(~SEX, nrow=1, scales="fixed") +
        theme(
          axis.text.x = element_text(size = 10, color="#000000"),
          axis.text.y = element_text(size = 10, color="#000000"),
          axis.title.x = element_text(size = 10, color="#000000"),
          axis.title.y = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=10, color="#000000", hjust=0.5),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "none") +
        geom_density(alpha=.2) +
        ylab("Probability  Density") +
        xlab("Satisfaction Level") + 
        ggtitle("")
```

```{r fig.height = 4, fig.width = 6, fig.align = "center"}
p3
```


#### Distribution of Satisfaction Level (by Ethnicity and Sex)
```{r}
p4 <- ggplot(dat, aes(x=SATISFACTION_LEVEL)) +
        geom_histogram(aes(y=..density..), position="identity", color="#FFFFFF", fill="#377eb8", bins=10) +
        scale_x_continuous(breaks=seq(0,10,by=1)) +
        facet_grid(SEX~ETHNICITY, scales="fixed") +
        theme(
          axis.text.x = element_text(size = 8, color="#000000"),
          axis.text.y = element_text(size = 8, color="#000000"),
          axis.title.x = element_text(size = 10, color="#000000"),
          axis.title.y = element_text(size = 10, color="#000000"),
          plot.title = element_text(size = 10, color="#000000", hjust=0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.ticks = element_line(size=0.4, color="#000000"),	
          strip.text = element_text(size=9, color="#000000", hjust=0.5),
          strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
          panel.background = element_rect(fill="#FFFFFF", color="#000000"),
          legend.text = element_text(size = 10, color="#000000"),
          legend.title = element_blank(),
          legend.key.size = unit(0.5, "cm"),
          legend.position = "none") +
        geom_density(alpha=.2)+ 
        ylab("Probability  Density") +
        xlab("Satisfaction Level") + 
        ggtitle("")
```

```{r fig.height = 5, fig.width = 10, fig.align = "center"}
p4
```

```{r fig.height = 5, fig.width = 6.5, fig.align = "center"}
pl_den <- grid.arrange(p1, p4, ncol=1)
```


### Correlation between mean satisfaction and Gini-Simpson of income by Ethnicity
```{r}
df3$Satisfaction_Mean
dat_eth <-data.frame(Ethnicity = c("Bahun", "Chettri", "Dalit", "Gurung", "Newar", "Tamang"),
                  IC1 = c(2, 3, 6, 7, 2, 11), 
                  IC2 = c(13, 17, 17, 22, 18, 61),
                  IC3 = c(9, 18, 20, 30,8, 35),
                  IC4 = c(13, 10, 4, 18, 8, 17),
                  IC5 = c(1, 3, 0, 4, 0, 0),
                  IC6 = c(2, 1, 0, 0, 0, 1))
eth_simpson <- diversity(dat_eth[2:7], index = "simpson")
shapiro.test(eth_simpson)
cor.test(df3$Satisfaction_Mean, eth_simpson, method="pearson")
```