---
title: "Regression Analysis: Satisfaction with New Houses"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'regression_analysis.html'))})
---


#### Define Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE}
library("stringr")
library("MASS")
library("dplyr")
library("car")
library("knitr")
library("effects")
library("ggplot2")
library("gridExtra")
library("brant")
library("VGAM")
library("sandwich")
library("bucky")
library("lmtest")
library("reshape2")
```

#### Define Path
```{r tidy=TRUE}
dir.wrk <- getwd()
dir.data <- file.path(dir.wrk, "dataset/data")
dir.annot <- file.path(dir.wrk, "dataset/annotation")
```

#### Define Files
```{r tidy=TRUE}
file.dat <- file.path(dir.data, "mastertbl_household_reconstruction.tsv")
```

#### Load Data
```{r tidy=TRUE}
dat <- read.delim(file.dat, header=TRUE, stringsAsFactors=FALSE)

# FACTORIZE ---
dat$DISTRICT <- factor(dat$DISTRICT, levels=c("Dhading","Sindhupalchowk"))
dat$VDC_MUN <- factor(dat$VDC_MUN, levels=c("Gumdi","Sertung","Batase","Pangtang"))
dat$WARD <- as.factor(dat$WARD)
dat$SEX <- factor(dat$SEX, levels=c("Male","Female"))
dat$ETHNICITY <- factor(dat$ETHNICITY, levels=c("Bahun","Chhetri","Dalit-Others","Gurung-Magar","Newar","Tamang"))
dat$EDUCATION_LEVEL <- factor(dat$EDUCATION_LEVEL, levels=c("Illiterate","Primary","Secondary","University"))
dat$OCCUPATION <- factor(dat$OCCUPATION, levels=c("Agriculture","Business","Goverment Employee","Labour","Teacher"))
dat$INCOME_LEVEL <- factor(dat$INCOME_LEVEL, levels=c("0-2.5K","2.5-10K","10-20K","20-40K","40-60K","60K-Above"))
dat$RECON_COMPLETED <- as.factor(dat$RECON_COMPLETED)
dat$SATISFACTION_LEVEL <- as.factor(dat$SATISFACTION_LEVEL)
dat$FREEDOM_CHOICE <- as.factor(dat$FREEDOM_CHOICE) 

#str(dat)
```
</br></br>

### Ordered Logistic Regression: Satisfaction Level vs. all Potential Predictors
```{r message=FALSE}
# FIT ORDERED LOGISTIC REGRESSION ---
dat$AGE_CATEGORY <- cut(dat$AGE, breaks=c(18, 29, 39, 49, 59, 69, 85), include.lowest=TRUE)

fit.mc <- MASS::polr(SATISFACTION_LEVEL ~ SEX + ETHNICITY + FREEDOM_CHOICE + EDUCATION_LEVEL + OCCUPATION + RECON_COMPLETED + DISTRICT + INCOME_LEVEL + AGE_CATEGORY + HOUSEHOLD_SIZE, data=dat, Hess=TRUE, method="logistic")

AIC(fit.mc)

# CALCULATE P-VALUE ---
summary_table <- coef(summary(fit.mc))
pval <- pnorm(abs(summary_table[, "t value"]), lower.tail=FALSE)* 2
summary_table <- cbind(summary_table, "p value"=round(pval,4))

# CALCULATE LOG-ODDS RATIO ---
tbl_oddratio <- exp(cbind(OddRatio=coef(fit.mc), confint(fit.mc, level=0.95)))

# AGGREGATE DATA ---
summary_table_var <- as.data.frame(cbind(summary_table[1:nrow(tbl_oddratio),], tbl_oddratio))

rmarkdown::paged_table(format(summary_table_var, digits=3), options=list(rows.print=10))  
```

### Analysis of deviance
```{r}
# ANOVA 
car::Anova(fit.mc)
```

The above analysis reveals that the effects of variables such as, location, education, income, physical level of reconstruction, and occupation on the self-reported satisfaction are not statistically significant (at 95% confidence level). However, the effects of variables such as, Sex, Ethnicity, and Freedom of Choice on the satisfaction level were found to be statistically significant. Thus, we perform the above analysis considering only Sex, Ethinicity, and Freedom of Choice.
</br></br>

### Ordered Logistic Regression: Satisfaction Level vs. Significant Predictors
```{r message=FALSE}
# FIT ORDERED LOGISTIC REGRESSION ---
fit.m <- MASS::polr(SATISFACTION_LEVEL ~ SEX+ETHNICITY+FREEDOM_CHOICE, data=dat, Hess=TRUE, method="logistic")

AIC(fit.m)

# CALCULATE P-VALUE ---
summary_table <- coef(summary(fit.m))
pval <- pnorm(abs(summary_table[, "t value"]), lower.tail=FALSE)* 2
summary_table <- cbind(summary_table, "p value"=round(pval,4))

# CALCULATE LOG-ODDS RATIO ---
tbl_oddratio <- exp(cbind(OddRatio=coef(fit.m), confint(fit.m, level=0.95)))

# AGGREGATE DATA ---
summary_table_var <- as.data.frame(cbind(summary_table[1:nrow(tbl_oddratio),], tbl_oddratio))

rmarkdown::paged_table(format(summary_table_var, digits=3), options=list(rows.print=10))  
```


```{r}
# SATISFACTION THRESHOLD ---
summary_table_st <- as.data.frame(summary_table[(nrow(tbl_oddratio)+1):nrow(summary_table),])
rmarkdown::paged_table(summary_table_st)
```

### Analysis of Deviance
```{r}
# ANOVA 
car::Anova(fit.m)
```

### Heteroscedasticity Robust Stdandard Errors and p-values 
```{r}
coef_t <- lmtest::coeftest(fit.m, vcov = sandwich::vcovHC(fit.m, type = "HC0"))

coef_t
```

### Odds Ratios with Robust Confidence Intervals
```{r}
robust_sr <- sqrt(diag( sandwich::vcovHC(fit.m, type = "HC0") ))
y_or <- exp(coef(fit.m))
robust_or <- suppressWarnings(
                cbind(coef_t, y_or, 
                   LL = exp(coef(fit.m) - 1.96 * robust_sr), 
                   UL = exp(coef(fit.m) + 1.96 * robust_sr)))

knitr::kable(format(as.data.frame(robust_or), digits=3), align="lllllll")
```

</br></br>

### Satistfaction Level for each Level of Freedom of Choice
```{r}
# EFFECT OF THE FITTED MODEL ---
ef1 <- effects::Effect(focal.predictors="FREEDOM_CHOICE", mod=fit.m, 
                       xlevels=list(FREEDOM_CHOICE = 1:10, 2), latent = TRUE)

#plot(ef1, rug=FALSE)
```


```{r}
#### FUNCTION: plotEffect()
plotEffect <- function(ef.obj){
  # PREPARE DATA ---
  df <- cbind(ef.obj$x, fit=ef.obj$fit, upper=ef.obj$upper, lower=ef.obj$lower)
  dt <- data.frame(Level=names(ef.obj$thresholds), thresholds=ef.obj$thresholds)
  
  # FACTORIZE ---
  df$FREEDOM_CHOICE <- as.numeric(as.character(df$FREEDOM_CHOICE))
  
  # PLOT ---
  p <- ggplot(data = df, aes(x=FREEDOM_CHOICE, y=fit)) +
              geom_hline(yintercept = dt$thresholds[5:9], color="#D9D9D9", size=1, linetype=2) +
              #geom_ribbon(aes(ymin=lower, ymax=upper), fill="#D9D9D9", alpha=0.5) +
              geom_line(aes(y = fit), color="#E31A1C", size=1.5) +
              geom_errorbar(data=df, aes(x=FREEDOM_CHOICE, ymin=upper, ymax=lower), width=0.2, size=1, color="#969696") +
              geom_point(color="#E31A1C", size=3) +
              scale_x_continuous(breaks=c(1:10), labels=c(1:10)) +
              scale_y_continuous(breaks=dt$thresholds,  labels=dt$Level, name="Satisfaction Level",
                    sec.axis=sec_axis(~.*1,name="Effect", breaks=seq(-2,4,1), labels=seq(-2,4,1))) +
              theme(
                axis.text.x = element_text(size = 10, color="#000000"),
                axis.text.y = element_text(size = 10, color="#000000"),
                axis.title = element_text(size = 10, color="#000000"),
                plot.title = element_text(size = 10, color="#000000", hjust=0.5),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                axis.ticks = element_line(size=0.4, color="#000000"),	
                strip.text = element_text(size=10, color="#000000"),
                strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
                panel.background = element_rect(fill="#FFFFFF", color="#000000"),
                legend.text = element_text(size = 10, color="#000000"),
                legend.title = element_blank(),
                legend.key.size = unit(0.5, "cm"),
                legend.position = "none") +
            ylab("Effect") +
            xlab("Freedom of Choice") + 
            ggtitle("")
            
    return(p)
}
```

```{r fig.height = 4, fig.width = 6, fig.align = "center"}
plotEffect(ef.obj=ef1)
```

</br></br>

### Satistfaction Level vs. Freedom of Choice by Sex and Ethnicity
```{r}
# EFFECT OF THE FITTED MODEL ---
ef2 <- effects::Effect(focal.predictors=c("SEX","FREEDOM_CHOICE","ETHNICITY"), mod=fit.m, 
                       xlevels=list(FREEDOM_CHOICE = 1:10), latent = TRUE)

#plot(ef2, rug = FALSE, ylim = c(-2.0,4.5))
```


```{r}
# FUNCTION: plotEffect_MultiVar()
plotEffect_MultiVar <- function(ef.obj){
  # PREPARE DATA ---
  df <- cbind(ef.obj$x, fit=ef.obj$fit, upper=ef.obj$upper, lower=ef.obj$lower)
  dt <- data.frame(Level=names(ef.obj$thresholds), thresholds=ef.obj$thresholds)
  
  # FACTORIZE ---
  df$FREEDOM_CHOICE <- as.numeric(as.character(df$FREEDOM_CHOICE))
  df$SEX <- factor(df$SEX, levels=c("Male","Female"))
  df$ETHNICITY <- factor(df$ETHNICITY, levels=c("Bahun","Chhetri","Dalit-Others","Gurung-Magar","Newar","Tamang"))

  # PLOT ---
  p <- ggplot(data = df, aes(x=FREEDOM_CHOICE, y=fit)) +
              geom_hline(yintercept = dt$thresholds[4:9], color="#D9D9D9", size=1, linetype=2) +
              #geom_ribbon(aes(ymin=lower, ymax=upper), fill="#D9D9D9", alpha=0.5) +
              geom_line(aes(y = fit), color="#E31A1C", size=2) +
              geom_errorbar(data=df, aes(x=FREEDOM_CHOICE, ymin=upper, ymax=lower), width=0.2, size=1, color="#969696") +
              geom_point(color="#E31A1C", size=2) +
              scale_x_continuous(breaks=c(1:10), labels=c(1:10)) +
              scale_y_continuous(breaks=dt$thresholds,  labels=dt$Level, name="Satisfaction Level",
                    sec.axis=sec_axis(~.*1,name="Effect", breaks=seq(-2,4,1), labels=seq(-2,4,1))) +
              #facet_grid(ETHNICITY~SEX, scales="fixed", space="fixed") +
              facet_grid(SEX~ETHNICITY, scales="fixed", space="fixed") +
              theme(
                axis.text.x = element_text(size = 10, color="#000000"),
                axis.text.y = element_text(size = 10, color="#000000"),
                axis.title = element_text(size = 10, color="#000000"),
                plot.title = element_text(size = 10, color="#000000", hjust=0.5),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                axis.ticks = element_line(size=0.4, color="#000000"),	
                strip.text = element_text(size=10, color="#000000"),
                strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
                panel.background = element_rect(fill="#FFFFFF", color="#000000"),
                legend.text = element_text(size = 10, color="#000000"),
                legend.title = element_blank(),
                legend.key.size = unit(0.5, "cm"),
                legend.position = "none") +
            ylab("Effect") +
            xlab("Freedom of Choice") + 
            ggtitle("")
    return(p)
}
```


```{r fig.height = 6, fig.width = 12, fig.align = "center"}
plotEffect_MultiVar(ef.obj=ef2)
```

</br></br>

```{r}
ef3 <- effects::Effect(focal.predictors="FREEDOM_CHOICE", mod=fit.m, 
                       xlevels=list(FREEDOM_CHOICE = 1:10, 2))

#plot(ef3, lines=list(multiline=TRUE), rug=FALSE)
```

</br></br>

### Propbability of Each Level of Satisfaction at Different Freedom Levels
```{r}
#### FUNCTION: plotEffect()
plotProbEffect <- function(ef.obj){
  # PREPARE DATA ---
  df <- cbind(ef.obj$x, ef.obj$prob)
  
  # RESHAPE DATA ---
  dm <- reshape2::melt(df, id.vars="FREEDOM_CHOICE", value.name="PROBABILITY")
  colnames(dm) <- c("FREEDOM_CHOICE","SATISFACTION_LEVEL","PROBABILITY")
  dm$SATISFACTION_LEVEL <- str_replace_all(dm$SATISFACTION_LEVEL, "prob.X", "")
  
  # FACTORIZE ---
  dm$FREEDOM_CHOICE <- as.numeric(as.character(dm$FREEDOM_CHOICE))
  dm$SATISFACTION_LEVEL <- as.factor(as.numeric(dm$SATISFACTION_LEVEL))
  
  # COLOR PALETTE
  cpalette <- rev(c("#e31a1c","#a6cee3","#1f78b4","#b2df8a","#33a02c",
                  "#fb9a99","#fdbf6f","#ff7f00","#cab2d6","#6a3d9a"))
  # PLOT ---
  p <- ggplot(data = dm, aes(x=FREEDOM_CHOICE, y=PROBABILITY)) +
              geom_line(aes(y=PROBABILITY, color=SATISFACTION_LEVEL), size=1.5) +
              geom_point(aes(y=PROBABILITY, color=SATISFACTION_LEVEL), size=3) +
              scale_x_continuous(breaks=c(1:10), labels=c(1:10)) +
              scale_y_continuous(breaks=seq(0,0.6,0.1)) +
              scale_color_manual(values=cpalette, name="Satisfaction Level") +
              theme(
                axis.text.x = element_text(size = 10, color="#000000"),
                axis.text.y = element_text(size = 10, color="#000000"),
                axis.title = element_text(size = 10, color="#000000"),
                plot.title = element_text(size = 10, color="#000000", hjust=0.5),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                axis.ticks = element_line(size=0.4, color="#000000"),	
                strip.text = element_text(size=10, color="#000000"),
                strip.background = element_rect(fill="#FFFFFF", color="#FFFFFF"),
                panel.background = element_rect(fill="#FFFFFF", color="#000000"),
                legend.text = element_text(size = 10, color="#000000"),
                legend.title = element_text(size = 10, color="#000000"),
                legend.key.size = unit(0.5, "cm"),
                legend.background = element_blank(),
                legend.box.background = element_blank(),
                legend.position = "bottom") +
            ylab("Probability of Satisfaction") +
            xlab("Freedom of Choice") + 
            ggtitle("")
    return(p)
}
```

```{r fig.height = 6, fig.width = 6, fig.align = "center"}
plotProbEffect(ef.obj=ef3)
```

</br></br>

### Check for Proportional or Parallel Assumption
```{r}
suppressWarnings(brant(fit.m))
```

</br></br>

### Proportional Assumption Check with VGAM
```{r}
m_glm <- suppressWarnings(VGAM::vglm(SATISFACTION_LEVEL~FREEDOM_CHOICE+ETHNICITY+SEX, data = dat,
                    family = VGAM::cumulative(link = "logitlink", parallel = TRUE, reverse = FALSE)))
```

```{r}
Anova(m_glm)
summary(m_glm)
is.parallel(m_glm)
```

## Check for Multicollinearity: polr Model
```{r}
car::vif(fit.m)
```

### Ordered Logistic Regression with FREEDOM as Dependent Variable
```{r message=FALSE}
# FIT FREEDOM ---
dat$FREEDOM_CHOICE <- as.numeric(dat$FREEDOM_CHOICE)
fit.free <- lm(FREEDOM_CHOICE ~ SEX+ETHNICITY, data=dat)
summary(fit.free)

# CALCULATE P-VALUE ---
summary_table <- coef(summary(fit.free))
pval <- pnorm(abs(summary_table[, "t value"]), lower.tail=FALSE)* 2
summary_table <- cbind(summary_table, "p value"=round(pval,4))
```


### Ordered Logistic Regression with Freedom Level 9 as Reference
```{r message=FALSE}
# FIT ORDERED LOGISTIC REGRESSION ---
dat$SATISFACTION_LEVEL <- as.factor(dat$SATISFACTION_LEVEL)
dat$FREEDOM_CHOICE <- as.factor(dat$FREEDOM_CHOICE) 
dat9 <- within(dat, FREEDOM_CHOICE <- relevel(FREEDOM_CHOICE, ref = 9))

fit.m9 <- MASS::polr(SATISFACTION_LEVEL ~ SEX+ETHNICITY+FREEDOM_CHOICE, data=dat9, Hess=TRUE, method="logistic")
```

### Heteroscedasticity Robust Standard Errors and p-values 
```{r}
coef_t9 <- lmtest::coeftest(fit.m9, vcov = sandwich::vcovHC(fit.m9, type = "HC0"))
```

### Odds Ratios with Robust 95% CI
```{r}
robust_sr <- sqrt(diag( sandwich::vcovHC(fit.m9, type = "HC0") ))
y_or <- exp(coef(fit.m9))
robust_or <- suppressWarnings(
                cbind(coef_t9, y_or, 
                   LL = exp(coef(fit.m9) - 1.96 * robust_sr), 
                   UL = exp(coef(fit.m9) + 1.96 * robust_sr)))

knitr::kable(format(as.data.frame(robust_or), digits=3), align="lllllll")
```
