---
title: "Robustness Check"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'robustness check.html'))})
---


#### Define Libraries
```{r echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE}
library("stringr")
library("MASS")
library("dplyr")
library("car")
library("knitr")
library("effects")
library("ggplot2")
library("gridExtra")
library("brant")
library("VGAM")
library("sandwich")
library("bucky")
library("lmtest")
library("reshape2")
```

#### Define Path
```{r tidy=TRUE}
dir.wrk <- getwd()
dir.data <- file.path(dir.wrk, "dataset/data")
dir.annot <- file.path(dir.wrk, "dataset/annotation")
```

#### Define Files
```{r tidy=TRUE}
file.dat <- file.path(dir.data, "mastertbl_household_reconstruction.tsv")
```

#### Load Data
```{r tidy=TRUE}
dat <- read.delim(file.dat, header=TRUE, stringsAsFactors=FALSE)

# FACTORIZE ---
dat$DISTRICT <- factor(dat$DISTRICT, levels=c("Dhading","Sindhupalchowk"))
dat$VDC_MUN <- factor(dat$VDC_MUN, levels=c("Gumdi","Sertung","Batase","Pangtang"))
dat$WARD <- as.factor(dat$WARD)
dat$SEX <- factor(dat$SEX, levels=c("Male","Female"))
dat$ETHNICITY <- factor(dat$ETHNICITY, levels=c("Bahun","Chhetri","Dalit-Others","Gurung-Magar","Newar","Tamang"))
dat$EDUCATION_LEVEL <- factor(dat$EDUCATION_LEVEL, levels=c("Illiterate","Primary","Secondary","University"))
dat$OCCUPATION <- factor(dat$OCCUPATION, levels=c("Agriculture","Business","Goverment Employee","Labour","Teacher"))
dat$INCOME_LEVEL <- factor(dat$INCOME_LEVEL, levels=c("0-2.5K","2.5-10K","10-20K","20-40K","40-60K","60K-Above"))
dat$RECON_COMPLETED <- as.factor(dat$RECON_COMPLETED)
dat$SATISFACTION_LEVEL <- as.factor(dat$SATISFACTION_LEVEL)

```
</br></br>

### Robustness Check: Ordered Logistic Regression with Freedom as Continuous Variable
```{r message=FALSE}
# FIT ORDERED LOGISTIC REGRESSION ---
fit.m1 <- MASS::polr(SATISFACTION_LEVEL ~ SEX + ETHNICITY + FREEDOM_CHOICE, data=dat, Hess=TRUE, method="logistic")

# CALCULATE P-VALUE ---
summary_tab <- coef(summary(fit.m1))
pvalue <- pnorm(abs(summary_tab[, "t value"]), lower.tail=FALSE)* 2
summary_tab <- cbind(summary_tab, "p value"=round(pvalue,4))

# CALCULATE LOG-ODDS RATIO ---
tbl_oddratio <- exp(cbind(OddRatio=coef(fit.m1), confint(fit.m1, level=0.95)))

# AGGREGATE DATA ---
summary_tab_var <- as.data.frame(cbind(summary_tab[1:nrow(tbl_oddratio),], tbl_oddratio))

rmarkdown::paged_table(format(summary_tab_var, digits=3), options=list(rows.print=10))  
```

### Analysis of deviance
```{r}
# ANOVA 
car::Anova(fit.m1)
```

### Heteroscedasticity Robust stdandard errors and p-values 
```{r}
coef_t <- lmtest::coeftest(fit.m1, vcov = sandwich::vcovHC(fit.m1, type = "HC0"))
coef_t
```
### Odds Ratios with Robust Confidence Intervals
```{r}
robust_sr <- sqrt(diag(sandwich::vcovHC(fit.m1, type = "HC0") ))
y_or <- exp(coef(fit.m1))
robust_or <- suppressWarnings(
                cbind(coef_t, y_or, 
                   LL = exp(coef(fit.m1) - 1.96 * robust_sr), 
                   UL = exp(coef(fit.m1) + 1.96 * robust_sr)))

knitr::kable(format(as.data.frame(robust_or), digits=3), align="lllllll")
```

### Robustness Check: Ordered Logistic Regression with Reconstruction Completed as Additional Control
```{r message=FALSE}

dat$FREEDOM_CHOICE <- as.factor(dat$FREEDOM_CHOICE)
# FIT ORDERED LOGISTIC REGRESSION ---
fit.m2 <- MASS::polr(SATISFACTION_LEVEL ~ SEX+ETHNICITY+FREEDOM_CHOICE+RECON_COMPLETED, data=dat, Hess=TRUE, method="logistic")

# CALCULATE P-VALUE ---
summary_tab <- coef(summary(fit.m2))
pvalue <- pnorm(abs(summary_tab[, "t value"]), lower.tail=FALSE)* 2
summary_tab <- cbind(summary_tab, "p value"=round(pvalue,4))

# CALCULATE LOG-ODDS RATIO ---
tbl_oddratio <- exp(cbind(OddRatio=coef(fit.m2), confint(fit.m2, level=0.95)))

# AGGREGATE DATA ---
summary_table_var <- as.data.frame(cbind(summary_tab[1:nrow(tbl_oddratio),], tbl_oddratio))

rmarkdown::paged_table(format(summary_table_var, digits=3), options=list(rows.print=10))  
```

```{r}
# SATISFACTION THRESHOLD ---
summary_table_st <- as.data.frame(summary_tab[(nrow(tbl_oddratio)+1):nrow(summary_tab),])
rmarkdown::paged_table(summary_table_st)
```

### Analysis of deviance
```{r}
# ANOVA 
car::Anova(fit.m2)
```

### Heteroscedasticity Robust stdandard errors and p-values 
```{r}
coef_t <- lmtest::coeftest(fit.m2, vcov = sandwich::vcovHC(fit.m2, type = "HC0"))
coef_t
```
### Odds Ratios with Robust Confidence Intervals
```{r}
robust_sr <- sqrt(diag( sandwich::vcovHC(fit.m2, type = "HC0") ))
y_or <- exp(coef(fit.m2))
robust_or <- suppressWarnings(
                cbind(coef_t, y_or, 
                   LL = exp(coef(fit.m2) - 1.96 * robust_sr), 
                   UL = exp(coef(fit.m2) + 1.96 * robust_sr)))

knitr::kable(format(as.data.frame(robust_or), digits=3), align="lllllll")
```

### Robustness Check: Ordered Logistic Regression with freedonm as continuous variable and Reconstruction Completed as additional Control
```{r message=FALSE}

dat$FREEDOM_CHOICE <- as.numeric(dat$FREEDOM_CHOICE)
# FIT ORDERED LOGISTIC REGRESSION ---
fit.m3 <- MASS::polr(SATISFACTION_LEVEL ~ SEX+ETHNICITY+FREEDOM_CHOICE+RECON_COMPLETED, data=dat, Hess=TRUE, method="logistic")

# CALCULATE P-VALUE ---
summary_tab <- coef(summary(fit.m3))
pvalue <- pnorm(abs(summary_tab[, "t value"]), lower.tail=FALSE)* 2
summary_tab <- cbind(summary_tab, "p value"=round(pvalue,4))

# CALCULATE LOG-ODDS RATIO ---
tbl_oddratio <- exp(cbind(OddRatio=coef(fit.m3), confint(fit.m3, level=0.95)))

# AGGREGATE DATA ---
summary_table_var <- as.data.frame(cbind(summary_tab[1:nrow(tbl_oddratio),], tbl_oddratio))

rmarkdown::paged_table(format(summary_table_var, digits=3), options=list(rows.print=10))  
```

```{r}
# SATISFACTION THRESHOLD ---
summary_table_st <- as.data.frame(summary_tab[(nrow(tbl_oddratio)+1):nrow(summary_tab),])
rmarkdown::paged_table(summary_table_st)
```

### Analysis of deviance
```{r}
# ANOVA 
car::Anova(fit.m3)
```

### Heteroscedasticity Robust stdandard errors and p-values 
```{r}
coef_t <- lmtest::coeftest(fit.m3, vcov = sandwich::vcovHC(fit.m3, type = "HC0"))
coef_t
```
### Odds Ratios with Robust Confidence Intervals
```{r}
robust_sr <- sqrt(diag( sandwich::vcovHC(fit.m2, type = "HC0") ))
y_or <- exp(coef(fit.m3))
robust_or <- suppressWarnings(
                cbind(coef_t, y_or, 
                   LL = exp(coef(fit.m3) - 1.96 * robust_sr), 
                   UL = exp(coef(fit.m3) + 1.96 * robust_sr)))

knitr::kable(format(as.data.frame(robust_or), digits=3), align="lllllll")
```


### OLS Model with Freedom as Categorical Variable
```{r}
dat$SATISFACTION_LEVEL <- as.numeric(dat$SATISFACTION_LEVEL)
dat$FREEDOM_CHOICE <- as.factor(dat$FREEDOM_CHOICE)
fit_lin <- lm(SATISFACTION_LEVEL~SEX+ETHNICITY+FREEDOM_CHOICE, data=dat)

lmtest::coeftest(fit_lin, vcov = sandwich::vcovHC(fit_lin, type = "HC0"))
```

### OLS Model with Freedom as Categorical Variable and Reconstruction Completed as an Additional Control
```{r}
dat$SATISFACTION_LEVEL <- as.numeric(dat$SATISFACTION_LEVEL)
dat$FREEDOM_CHOICE <- as.factor(dat$FREEDOM_CHOICE)
fit_lin <- lm(SATISFACTION_LEVEL~SEX+ETHNICITY+FREEDOM_CHOICE+RECON_COMPLETED, data=dat)

lmtest::coeftest(fit_lin, vcov = sandwich::vcovHC(fit_lin, type = "HC0"))
```

### OLS Model with Freedom as Continuous Variable
```{r}
dat$SATISFACTION_LEVEL <- as.numeric(dat$SATISFACTION_LEVEL)
dat$FREEDOM_CHOICE <- as.numeric(dat$FREEDOM_CHOICE)

fit_lin <- lm(SATISFACTION_LEVEL~SEX+ETHNICITY+FREEDOM_CHOICE, data=dat)

lmtest::coeftest(fit_lin, vcov = sandwich::vcovHC(fit_lin, type = "HC0"))
```

### OLS Model with Freedom as Continuous Variable and Reconstruction Completed as an Additional Control 
```{r}
dat$SATISFACTION_LEVEL <- as.numeric(dat$SATISFACTION_LEVEL)
dat$FREEDOM_CHOICE <- as.numeric(dat$FREEDOM_CHOICE)
fit_lin <- lm(SATISFACTION_LEVEL~SEX+ETHNICITY+FREEDOM_CHOICE+RECON_COMPLETED, data=dat)

lmtest::coeftest(fit_lin, vcov = sandwich::vcovHC(fit_lin, type = "HC0"))
```